---
title: "Colleges"
format: html
author: Anthony Gao
execute:
    echo: false
---

Colleges vary widely in their graduation rates, and tuition is one factor that may help explain those differences so students can end up for a place where they can succeedom. Using 2013 IPEDS data on nearly 900 U.S. four-year colleges, we estimate the difference in expected graduation rate between colleges that charge $20,000 in tuition and those that charge $30,000.

```{r}
#| label: setup
#| message: false
library(tidyverse)
library(primer.data)
```

## Tuition and Graduation Rate

We now examine how the graduation rate varies with the cost of tuition.

```{r}
#| label: plot-grad-rate-vs-tuition
#| warning: false
colleges |> 
  ggplot(aes(x = tuition, y = grad_rate)) +
  geom_point(alpha = 0.4) +
  geom_smooth(method = "loess", formula = "y ~ x", se = FALSE) +
  labs(
    title = "Graduation Rate vs. Tuition",
    x = "Tuition (in tens of thousands of dollars)",
    y = "Graduation Rate"
  )
```

```{r}
#| label: clean-data
#| cache: true
x <- colleges |> 
  select(tuition, grad_rate, selectivity) |> 
  filter(tuition > 2) |> 
  drop_na() |> 
  mutate(selectivity = factor(selectivity, 
                              levels = c("Elite", "Highly Selective", "Moderately Selective", "Lowly Selective", "Non-selective"), 
                              ordered = FALSE))
```


